---
title: "Informe práctica 4 - Constructing Single Cell Trajectories with Monocle3"
author: "Adam Casas"
date: 'Compilado: `r format(Sys.Date(), "%d de %B del %Y")`'
output: 
  html_document:
    df_print: paged
    highlight: kate
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
---

```{r configuracion_inicial, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = F,
                      warning = F,
                      tidy = F)
##################################################
#######        Encoded in UTF-8        ###########
##################################################
```

***

# Constructing Single Cell Trajectories with Monocle3


In this practical we will use the Nakamura dataset ( Practical 1 ) to infer a differentiation (developmental) trajectory from the data using Monocle3. This exercise is based on the Tutorial 1 found at:
http://cole-trapnell-lab.github.io/monocle-release/monocle3/. The web includes installation instructions.

# Introducción
  
```{r, message = F}
library("SingleCellExperiment")
library("TSCAN")
library("destiny")
library("SLICER")
library("ouija")
library("scater")
library("ggplot2")
library("ggthemes")
library("ggbeeswarm")
library("corrplot")
# library("M3Drop")
# library("monocle)
set.seed(1)
```




# The Monocle 3 workflow

eee



## Step 1: Normalizing and pre-processing the data


e

## Step 2: Reducing the dimensionality of the data


ee


***

<br>

# sessionInfo()

<details>

<summary> __Click para mostrar__ </summary>

```{r, echo = F}
sessionInfo()
```

</details>